---
title: "Andres"
author: "Andrés A."
date: "today"
format: 
  html:
    fig-width: 8
    fig-height: 8
    code-fold: TRUE
---

## Why this graph ?

To analyze the tweets, we devised a controversial score. This score was formulated under the premise that a higher number of replies compared to likes indicates a more controversial tweet, while a higher number of likes relative to replies suggests greater agreement on the topic. Hence, we utilized the following formula to provide a clearer representation of the data.


$$ \text{Controversial Score} = \frac{\text{replies\_count}}{\text{likes\_count} + \text{retweets\_count} + 1}$$
Therefore: 

- As we move towards the right, the tweet have more likes.
- As we move towards the top, the tweet becomes increasingly controversial.

Limitation:

- Tweets with a low number of likes were excluded due to challenges in calculating scores accurately.
- The use of log visualization could potentially lead to misinterpretation.


## Visual representation

```{r}
#| warning: false
#| include: false

rm(list = ls())
library(tidyverse)
library(plotly)
library(knitr)
library(DT)
library(crosstalk)

dr <- read_rds("../Data/tweets.rds")
source("../Andres/Andres_function.R")
```


```{r}
#| label: fig-Plot1
#| fig-cap: "Visual representation of tweets"


df_shared <- SharedData$new(df, key = ~likes_count)


p <- df_shared %>% 
  ggplot(aes(likes_count, score, color = score, 
             text = paste("score:",round(score,2),"\n",
                          "Likes:",round(likes_count,2),"\n",
                          "replies:",round(replies_count,2),"\n",
                          tweet_content )
             )
  ) + 
  geom_point()+
  scale_color_gradient(low = 'green',high = "red",transform = "log10") +
  scale_x_log10() + 
  scale_y_log10() + 
  labs(x = "Number of likes", 
       y = "Controversial Score")

ggplotly(p, tooltip ="text")

```
 
# Tabular representation 
 
```{r,include=T}
#| fig-cap: "Table"
#| warning: false

t <- df_shared %>% 
  DT::datatable(colnames = c("date","score","likes_count","replies_count","tweet","URL"),
                options = list(paging = T, 
                               pageLength = 20,
                               dom = "t",
                               scrollX = TRUE),
                rownames = FALSE,
                filter = 'top',
                escape = F)


t

```
